Supplementary Information 1

### 2025-03-28 MS2_Krill.Rmd
last changes in MS

# M&M

#### **2.1. Study Area and Data Sources**  
This study focuses on the Antarctic Peninsula, a region where krill populations exhibit strong variability due to environmental fluctuations and intense predation pressure. Data were obtained from the Commission for the Conservation of Antarctic Marine Living Resources (CCAMLR), including fishery-dependent catch data, scientific surveys, and predator monitoring datasets. Environmental data, such as sea surface temperature (SST), chlorophyll-a concentration, and sea ice extent, were sourced from satellite observations and oceanographic monitoring programs.

#### **2.2. Catch-to-Length Model Implementation**  
We applied an integrated Catch-to-Length model to estimate krill stock-recruitment relationships and population trends. The model links catch-at-length data with growth, mortality, and recruitment processes while incorporating environmental and predation variables. Key model parameters include:

- Growth rates based on length-frequency distributions  
- Natural mortality estimates derived from predator consumption data  
- Stock-recruitment functions incorporating environmental predictors  
- Fishery removals as a function of effort and environmental conditions

#### **2.3. Statistical Analysis and Model Validation**  
Model performance was evaluated through likelihood-based comparisons, sensitivity analyses, and cross-validation against independent survey datasets. We tested multiple scenarios to assess the relative influence of environmental and predation variables on recruitment and biomass dynamics.

### **3. Results**  
Our model results indicate that ecosystem variables significantly influence krill productivity and population structure:

1. **Stock-Recruitment Relationship**: Recruitment was positively correlated with sea ice extent and primary productivity, suggesting a strong link between krill reproduction and environmental conditions.  
2. **Predation Impact**: Penguin predation exerted a measurable effect on juvenile krill survival, with increased predation pressure leading to lower recruitment estimates in years with high predator abundance.  
3. **Biomass Trends**: Environmental drivers accounted for a substantial portion of biomass fluctuations, with warm years showing lower krill abundance, likely due to reduced primary productivity.  
4. **Fisheries Interaction**: Years with high krill harvest coincided with lower biomass estimates, highlighting the cumulative impact of both natural and anthropogenic pressures on krill stocks.

### **Tablas a incluir**
1. **Comparación de parámetros clave entre escenarios:**
   - Biomasa desovante (SSB, Spawning Stock Biomass) en años clave.
   - Tasa de explotación (F).
   - Reclutamiento medio.
   - Relación B/B0 (biomasa actual respecto a la virgen).
   - Relación F/FMSY.

2. **Resumen del ajuste del modelo:**
   - Log-verosimilitud total.
   - Verosimilitud de los datos de captura, índices de abundancia y composición de tallas/edades.
   - Número de parámetros estimados.
   - Error estándar de las estimaciones clave.

3. **Comparación de reclutamiento por año:**
   - Media y desviación estándar del reclutamiento en periodos clave (por ejemplo, 1990-2000, 2000-2010, 2010-2020).
   - Probabilidad de años de reclutamiento bajo.

### **Gráficos recomendados**
1. **Evolución de la biomasa desovante (SSB) en el tiempo**  
   - Líneas para cada escenario mostrando tendencias divergentes.
   - Inclusión de intervalos de confianza.

2. **Reclutamiento anual estimado por escenario**  
   - Barras para cada año con comparación entre escenarios.
   - Promedio móvil para suavizar tendencias.

3. **Relación stock-reclutamiento con diferentes ajustes**  
   - Ajustes de la curva con y sin variables ecosistémicas.
   - Comparación de la fuerza del reclutamiento en diferentes condiciones ambientales.

4. **Proyecciones de biomasa y F bajo diferentes escenarios de explotación**  
   - Predicciones de la biomasa y la explotación para los próximos 5-10 años.
   - Comparación entre políticas de manejo con y sin ecosistema.

5. **Distribución de longitudes o edades en el tiempo**  
   - Para ver si el escenario con variables ecosistémicas predice cambios en la estructura de la población.

6. **Curvas de Kobe plot (B/BMSY vs. F/FMSY)**  
   - Comparar el estado del stock en cada escenario respecto a puntos de referencia de manejo.

### **4. Discussion**  
Our findings emphasize the necessity of incorporating ecosystem variables into krill population assessments. The significant influence of environmental variability and predation highlights the limitations of traditional stock assessment models that assume static population processes.

- **Ecosystem-Based Management Implications**: Our study supports the integration of ecosystem-based reference points in krill fishery regulations. By considering environmental and predation effects, management frameworks can better anticipate population fluctuations and minimize risks of overexploitation.  
- **Predator-Krill Interactions**: The observed impact of penguin predation aligns with previous studies that indicate krill availability is a primary driver of penguin reproductive success. Managing krill fisheries in a way that ensures sufficient prey availability for predators is critical for maintaining ecosystem balance.  
- **Climate Change Considerations**: Given the ongoing warming trends in the Antarctic Peninsula, krill populations may face increased environmental stress. Our results suggest that future management strategies should incorporate climate-driven changes in krill habitat suitability.

### **5. Conclusion**  
This study demonstrates that incorporating environmental and predation variables into stock assessments significantly improves our understanding of Antarctic krill population dynamics. The integrated Catch-to-Length model provides a robust framework for assessing krill productivity under varying ecosystem conditions. Our results advocate for an ecosystem-based approach to krill fisheries management, ensuring that decision-making processes account for the broader ecological context.

### **Acknowledgments**  
We thank CCAMLR for providing access to data and acknowledge the support of the scientific community contributing to krill population research.

@@

@@

## Statistical model Stock Synthesis (SS3)

@@

@@

## Stock Assessment Scenarios

@@

| Scenario | Description                                                                          |
|:------------:|:---------------------------------------------------------|
|   s01    | Fishery and Survey (AMLR) data, Predator, Environmental data, aggregated at 48.1 level               |
|    s1    | Fishery and Survey (AMLR) Length data, CPUE, Catch by strata. Predator and Env data |
|    s2    | "s1" without Stock-Recruit relation                                      |
|    s3    | "s1" Beverton & Holt S-R relation weak (0.9 steepness)                   |
|    s4    | "s1" BH S-R relation strong (0.6 steepness)   |
|    s5    | "s1" BH S-R relation mid-strong estimated    |
|    s6    | "s1" Ricker S-R relation estimated    |
|    s7    | "s1" w/ set of parameters estimated in @Mardones2024par   |

@@

For the purposes of this working document, a comparative analysis of models `s01`, `s1` and `s7` will be evaluated, given that they contain elements such as aggregate data, spatially structured data and another set of life history parameters according to @Mardones2024par (unpublished).

>>>>

@@

## Study Area

@@

## Catch-to-Length Model Implementation

@@

We applied an integrated Catch-to-Length model to estimate krill stock-recruitment relationships and population trends. The model links catch-at-length data with growth, mortality, and recruitment processes while incorporating environmental and predation variables. Model performance was evaluated through likelihood-based comparisons, sensitivity analyses, and cross-validation.   
Key model parameters include:

### Natural Mortality and Growth Parameterization

The natural mortality rate (\(M\)) was specified using a single parameter per morphotype. Growth was modeled following a von Bertalanffy growth function with size-at-age parameterization. The model assumed linear growth below a predefined settlement age of 1.5 years. The asymptotic length (\(L_{\infty}\)) was determined by the estimated length-at-age of 999 years, indicating that the model used \(L_{\infty}\) as an upper growth boundary. Exponential decay of growth beyond maximum age was disabled (, ensuring that growth patterns followed the von Bertalanffy assumption without artificial constraints.

Growth variability was not explicitly modeled, and the coefficient of variation (CV) was assumed to be a function of length-at-age.

### Maturity and Reproduction

Maturity was modeled as an age-based logistic function, with the first age of maturity set at 3 years. Fecundity was estimated as a power function of body weight, where fecundity was computed as \(Eggs = Wt \times (a + b \times Wt)\). The model did not account for hermaphroditism, assuming that all individuals maintained a fixed sex throughout their lifespan.

The model used a direct parameterization approach for natural mortality (\(M\)), growth (\(G\)), and growth variability (\(CV_G\)), without additional offsets between sexes. Under this assumption, male parameters with a value of 0 and a negative estimation phase were set equal to their corresponding female parameters.

### Selectivity Parameterization

Selectivity functions were modeled using a length-based logistic formulation for the fishery, survey, and predator fleets. The selectivity curve was defined by two key parameters: the size at 50% selectivity (inflection point) and the width of the selection range (95% width).

The fishery was characterized by multiple selectivity patterns, each defined by an inflection point and a selection range width. The estimated inflection points varied between 2.0 and 3.5 cm, while the selection range widths spanned between 2.0 and 4.0 cm. Parameter estimation phases were assigned, with negative values indicating fixed parameters.

The survey selectivity was also modeled using a length-based logistic function. Inflection points ranged from 2.0 to 3.0 cm, with selection range widths consistently set at 1.0 cm. The phase assignment dictated whether parameters were freely estimated (positive phase values) or fixed (negative phase values).

The predator fleet followed a similar selectivity function, with a size-at-inflection point of 0.2 cm and a corresponding selection range width of 0.2 cm. These parameters were estimated in later phases (positive phase values), allowing flexibility in their estimation.

Across all selectivity functions, parameters with negative phase values were held fixed during the estimation process, ensuring model stability and preventing overparameterization.

### Spawner-Recruitment Relationship Parameterization

The stock-recruitment (SR) relationship was modeled using a standard Beverton-Holt formulation (option 3). This model was selected due to its robustness in representing recruitment dynamics in response to spawning biomass.

The unfished recruitment ($R_0$) was estimated with a log-transformed mean recruitment value ($SR\_LN(R_0)$) of 23, with a prior of 10. The parameter was freely estimated in phase 1. The steepness of the stock-recruitment curve ($SR\_BH\_steep$) was fixed at 0.85 in phase -4, ensuring consistency with previous studies. The standard deviation of recruitment deviations ($SR\_sigmaR$) was set at 1.2 and fixed in phase -4 to constrain model variability. The regime shift parameter ($SR\_regime$) was set at 0 and fixed, implying no consideration of long-term recruitment regime shifts. The $SR\_autocorr$ parameter was set to 0 and fixed, indicating that no temporal autocorrelation in recruitment deviations was assumed.

Recruitment deviations were estimated to account for interannual variability in recruitment dynamics. The model used the deviation vector approach ($do\_recdev = 1$), where recruitment was modeled as a function of spawning stock biomass plus a deviation term. The main recruitment deviation period spanned from 1998 to 2020, with forecast deviations applied in subsequent years.

The recruitment deviation phase was set to 2. Early recruitment deviations prior to 1998 were included, with an early deviation phase of -4 to ensure these values remained fixed. Bias adjustment was implemented, with key adjustment years defined as 1995.7 as the last early year with no bias adjustment, 2000.0 as the first year of full bias adjustment, 2015.7 as the last year of full bias adjustment, and 2022.3 as the first recent year with no bias adjustment. The maximum bias adjustment factor was 0.8274.

To prevent overparameterization, recruitment deviations were constrained between -5 and 5. No cyclic patterns in recruitment were assumed, and advanced recruitment options were enabled for model flexibility.

@@

### Stock Assessment Scenarios

@@

| Scenario | Description                                                                          |
|:------------:|:---------------------------------------------------------|
|    s1.1  | Spatial data without environmental and predator components                           |
|    s1.2  | "s1.1" with predator components                                                      |
|    s1.3  | "s1.1" with environmental variable                                              |
|    s1.4  | "s1.1" w/ both, predator fleet and environmental variable                        |

@@

## Results

Our model results indicate that ecosystem variables significantly influence krill productivity and population structure:

1. Stock-Recruitment Relationship: Recruitment was positively correlated with sea ice extent and primary productivity, suggesting a strong link between krill reproduction and environmental conditions.  
2. Predation Impact: Penguin predation exerted a measurable effect on juvenile krill survival, with increased predation pressure leading to lower recruitment estimates in years with high predator abundance.  
3. Biomass Trends: Environmental drivers accounted for a substantial portion of biomass fluctuations, with warm years showing lower krill abundance, likely due to reduced primary productivity.  
4. Fisheries Interaction: Years with high krill harvest coincided with lower biomass estimates, highlighting the cumulative impact of both natural and anthropogenic pressures on krill stocks.

### Tablas a incluir
1. Comparación de parámetros clave entre escenarios:
   - Biomasa desovante (SSB, Spawning Stock Biomass) en años clave.
   - Tasa de explotación (F).
   - Reclutamiento medio.
   - Relación B/B0 (biomasa actual respecto a la virgen).
   - Relación F/FMSY.

2. Resumen del ajuste del modelo:
   - Log-verosimilitud total.
   - Verosimilitud de los datos de captura, índices de abundancia y composición de tallas/edades.
   - Número de parámetros estimados.
   - Error estándar de las estimaciones clave.

3. Comparación de reclutamiento por año:
   - Media y desviación estándar del reclutamiento en periodos clave (por ejemplo, 1990-2000, 2000-2010, 2010-2020).
   - Probabilidad de años de reclutamiento bajo.

### Gráficos recomendados
1. Evolución de la biomasa desovante (SSB) en el tiempo  
   - Líneas para cada escenario mostrando tendencias divergentes.
   - Inclusión de intervalos de confianza.

2. Reclutamiento anual estimado por escenario  
   - Barras para cada año con comparación entre escenarios.
   - Promedio móvil para suavizar tendencias.

3. Relación stock-reclutamiento con diferentes ajustes  
   - Ajustes de la curva con y sin variables ecosistémicas.
   - Comparación de la fuerza del reclutamiento en diferentes condiciones ambientales.

4. Proyecciones de biomasa y F bajo diferentes escenarios de explotación  
   - Predicciones de la biomasa y la explotación para los próximos 5-10 años.
   - Comparación entre políticas de manejo con y sin ecosistema.

5. Distribución de longitudes o edades en el tiempo  
   - Para ver si el escenario con variables ecosistémicas predice cambios en la estructura de la población.

6. Curvas de Kobe plot (B/BMSY vs. F/FMSY)  
   - Comparar el estado del stock en cada escenario respecto a puntos de referencia de manejo.

### 4. Discussion  
Our findings emphasize the necessity of incorporating ecosystem variables into krill population assessments. The significant influence of environmental variability and predation highlights the limitations of traditional stock assessment models that assume static population processes.

- Ecosystem-Based Management Implications: Our study supports the integration of ecosystem-based reference points in krill fishery regulations. By considering environmental and predation effects, management frameworks can better anticipate population fluctuations and minimize risks of overexploitation.  
- Predator-Krill Interactions: The observed impact of penguin predation aligns with previous studies that indicate krill availability is a primary driver of penguin reproductive success. Managing krill fisheries in a way that ensures sufficient prey availability for predators is critical for maintaining ecosystem balance.  
- Climate Change Considerations: Given the ongoing warming trends in the Antarctic Peninsula, krill populations may face increased environmental stress. Our results suggest that future management strategies should incorporate climate-driven changes in krill habitat suitability.

### 5. Conclusion  
This study demonstrates that incorporating environmental and predation variables into stock assessments significantly improves our understanding of Antarctic krill population dynamics. The integrated Catch-to-Length model provides a robust framework for assessing krill productivity under varying ecosystem conditions. Our results advocate for an ecosystem-based approach to krill fisheries management, ensuring that decision-making processes account for the broader ecological context.

### Acknowledgments  
We thank CCAMLR for providing access to data and acknowledge the support of the scientific community contributing to krill population research.

### 2025-03-28 index.Rmd
last changes in MS

```{r }
SSplotData(base.model1.1, 
           subplot = 1,
           pheight = 15)

SSplotData(base.model1.2, 
           subplot = 1,
           pheight = 15)
```
# RESULTS

@@

SS_plots(base.model1.3, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

@@

```{r AKL, out.width='60%',  fig.cap="Representation of ALK Matrix to krill in 48.1"}
alk_matrix <- base.model1$ALK[,,1] # Ajusta las dimensiones según tu matriz

>>>>

```{r }
SSplotData(base.model1.1, 
           subplots = 1,
           pheight = 15)

SSplotData(base.model1.4, 
           subplots = 1,
           pheight = 15)
```
# RESULTS

@@

SS_plots(base.model1.3, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)

# S 1.4

# Definir la ruta de la carpeta
folder_path4 <- "s1.4/plots"
# Verificar si la carpeta existe y eliminarla
if (dir.exists(folder_path4)) {
  unlink(folder_path4, 
         recursive = TRUE)
  message("La carpeta 'plots' ha sido eliminada.")
} else {
  message("La carpeta 'plots' no existe.")
}

SS_plots(base.model1.4, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

@@

```{r AKL, out.width='60%',  fig.cap="Representation of ALK Matrix to krill in 48.1"}
alk_matrix <- base.model1.2$ALK[,,1] # Ajusta las dimensiones según tu matriz
